Technology for application family creation based on domain analysis

### 2016-05-13 2016-domainAnalysis/domainAnalysis.tex

As stated above, at present in many software companies the term ``domain analysis'' is understood as information gathering into some knowledge bases, but it is obvious that there are disadvantages of this approach. It may lead to incomplete glossary, absence of agreements about understanding some terms in the domain, so any misunderstanding of domain can result in an improper product. Therefore, several dozens of years ago were introduced some formal approaches for domain analysis. Here will be mentioned some of them. Main objective any domain analysis approach is to gain the domain model.

@@

As mentioned above, it was used QReal as DSM tool. A visual language was implemented there for describing feature models. Appropriate feature model for ``Joystick'' application family is proposed on Fig.~\ref{image:joystickFeatureModel}. This feature model presents explicit features, which are labeled as green, and some unite feature groups, which are labeled as blue. Type of arrow shows which feature is compulsory (shown as solid line with arrow on the end), which compulsory but there is some alternative between them (shown as dash line with an arrow on the end), and optional features, which may be implemented but not compulsory (shown as dash line with a circle on the end).

@@

Then with the aid of QReal tool a visual language was generated. Example of generated visual language is demonstrated on Fig.~\ref{image:joystickDsl}. It can be seen that in visual language editor can be specified property ``Quantity'', explicitly noting the concrete number of pads.

>>>>

As stated above, at present in many software companies the term ``domain analysis'' is understood as information gathering into some knowledge bases, but it is obvious that there are disadvantages of this approach. It may lead to incomplete glossary, absence of agreements about understanding some terms in the domain, so any misunderstanding of domain can result in an improper product. Therefore, several dozens of years ago were introduced some formal approaches for domain analysis. Here will be mentioned some of them. The main objective of any domain analysis approach is to produce the domain model.

@@

As mentioned above, it was used QReal as DSM tool. A visual language was implemented there for describing feature models. Appropriate feature model for ``Joystick'' application family is proposed on Fig.~\ref{image:joystickFeatureModel}. This feature model consists of explicit features, which are labeled green, and some feature groups, which are labeled blue. Type of arrow shows which feature is compulsory (shown as solid line with arrow on the end), which is compulsory but there is some alternative between them (shown as dash line with an arrow on the end), and optional features, which may be implemented but not compulsory (shown as dash line with a circle on the end).

@@

Then with the aid of QReal tool a visual language was generated. Example of generated visual language is demonstrated on Fig.~\ref{image:joystickDsl}. It can be seen that in visual language editor we can specify ``Quantity'' property, explicitly noting the concrete number of pads.
